Unsupervised training of maximum-entropy models for lexical selection in rule-based machine translation

### 2015-02-18 2015-eamt-melsa/2015-eamt-melsa.tex
more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58990 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{abstract}
  This article presents a method of training maximum-entropy models to
  perform lexical selection in a rule-based machine translation
  system. The training method described is unsupervised; that is, it
  does not require any annotated corpus. The method uses
  source-language monolingual corpora, the machine translation (MT)
  system in which the models are integrated and a statistical
  target-language model. Using the MT system, \todo{FSM: Check
    rewording! I have removed existing MT from this and previous
    sentence.} the sentences in the source-language corpus are
  translated in all possible ways according to the different
  translation equivalents in the bilingual dictionary of the system.
  These translations are then scored on the target-language model and
  the scores are normalised to provide fractional counts for training
  source-language maximum-entropy lexical-selection models. We show
  that these models can perform equally well, or better, than using
  the target-language model directly for lexical selection, at a
  substantially reduced computational cost.
\end{abstract}

>>>>

\begin{abstract}
  This article presents a method of training maximum-entropy models to
  perform lexical selection in a rule-based machine translation
  system. The training method described is unsupervised; that is, it
  does not require any annotated corpus. The method uses
  source-language monolingual corpora, the machine translation (MT)
  system in which the models are integrated and a statistical
  target-language model. Using the MT system, the sentences in 
  the source-language corpus are
  translated in all possible ways according to the different
  translation equivalents in the bilingual dictionary of the system.
  These translations are then scored on the target-language model and
  the scores are normalised to provide fractional counts for training
  source-language maximum-entropy lexical-selection models. We show
  that these models can perform equally well, or better, than using
  the target-language model directly for lexical selection, at a
  substantially reduced computational cost.
\end{abstract}
